\documentclass{article}
\usepackage{units}
\begin{document}

We are greatful to the reviewer for their insightful suggestions to improve our manuscript.
Included below are the the reviewer's suggested changes, and our modifications to the manuscript.

\section{Savitsky-Golay filtering}

From the reviewer:

\begin{quote}
The authors also use a well-tested filtering method for accounting for interference.
I am curious, though, why was this method chosen over others? I suspect it may be that it is straightforward, which reduces the possibility of introducing more errors and biases, but it is not clear.
\end{quote}
\noindent We have added the following to our description of the filtering method used:

\begin{quote}
  \input{sections/savitsky_golay.tex}
\end{quote}



\section{Wind gust}

From the reviewer:

\begin{quote}
  Although a ``gust of wind'' is mentioned, it is not clearly indicated in the data when that gust occurred, so it would be helpful to point that out if the timing is known.
\end{quote}

\noindent To address this issue, we have modified the caption of Figure 1 to indicate the timing of the wind gust:

\begin{quote}
  \input{sections/wind.tex}
\end{quote}

\noindent From the reviewer:

\begin{quote}
  Although something like that may not be possible to correct in the data analysis, it may be worth re-mentioning in the discussion where the radio light curve is compared to the theoretical curve.
\end{quote}

\noindent Because the wind gust occurred before the radio and optical lightcurves began to diverge, we have opted not to include further discussion of the wind gust in our comparison with theoretical lightcurves.

\section{Otsu thresholding}

From the reviewer:

\begin{quote}
  I would suggest, however, including a reference or very brief definition of Otsu thresholding.
\end{quote}

\noindent We have included the following reference: N. Otsu, “A threshold selection method from gray-level histograms,” IEEE Transactions on Systems, Man, and Cybernetics 9, 62–66 (1979)

\section{Model matching}

From the reviewer:

\begin{quote}
  It is not clear if the ``best fit curve'' was determined numerically or by eye
\end{quote}

\noindent The model was fit ``by eye.'' The following is not included in the theoretical lightcurve comparison section:

\begin{quote}
  \input{sections/model_matching.tex}
\end{quote}

\noindent From the reviewer:

\begin{quote}

  The variance in slope is particularly interesting! Is this also seen elsewhere in the literature?

\end{quote}

\noindent We have modified the conclusion as follows:

\begin{quote}
  \input{sections/model_slope.tex}
\end{quote}

\section{Comparison with other works}

From the reviewer:

\begin{quote}
  It is not clear why References 4 and 5 were chosen as the only reference points.
  I suspect it is because they were also measured at 1420 MHz and during a solar eclipse. If this is the case, it should be stated.
\end{quote}

\noindent We have included the following to the theoretical lightcurve comparison section:

\begin{quote}
  \input{sections/comparison_sources.tex}
\end{quote}

\noindent From the reviewer:

\begin{quote}
  The authors should also consider comparing it to the long history of measurements of solar radii at radio wavelengths through other methods, such as those listed in Menezes \& Valio (2018).
  Does this measurement fit the general trend of radius with frequency?
\end{quote}

\noindent We have added the following to our comparision with other works:

\begin{quote}
  \input{sections/history.tex}
\end{quote}

\section{Emission source}

\noindent From the reviewer:

\begin{quote}
  Finally, indicate, perhaps in the introduction or discussion, what kind of emission IS being given off in the radio that gives us this larger radius? (It’s not from the blackbody spectrum that dominates in the visible.)
\end{quote}

\noindent We have added the following to the introduction, after mentioning that the telescope is tuned to the spin-flip transition frequency of neutral hydrogen:

\begin{quote}
  \input{sections/emission.tex}
\end{quote}
  



\bibliography{refs}% Produces the bibliography via BibTeX.
\bibliographystyle{plain}

\end{document}

