\noindent Special thanks to these people for providing us the data necessary for our project:

% Come back and indent and make parentheses affiliations
\begin{enumerate}
    \item Scott Austin, Ph.D. (Director of Astronomical Facilities Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
    \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)
    \item Shane Ayotte. (UCA Mathematics Student)
\end{enumerate}

Technical Specifications of equipment used:
\begin{itemize}
    \item Optical Observations:
    \begin{itemize}
        \item Meade-14 LX200R on a Paramount MX+ equatorial mount
        \item Sony Alpha 6400 camera
        \item Sony FE 24mm-240mm f/3.5-6.3 lens
        \item NiSi Solar Filter Pro Nan UV/IR Cut ND 100000 72mm filter(Removed during Totality marked by 2460409.2849 JD and 2460409.2884 JD).
    \end{itemize}
    \item Radio Observations:
    \begin{itemize}
        \item Spider 230C: 2.3 meter aluminum dish, tuned to the spin-flip transition of HI at 1429.25 MHz.
        \item Mounted on a SkyWatcher EQ8-R Pro equatorial mount.
    \end{itemize}
\end{itemize}

References% Somehow make this bigger and make it in BibTex

\begin{enumerate}
    \item Stellarium \url{https://stellarium.org/}
    \item Messerotti, M., Zlobec, P., and Padovan, S. (2000). \textit{Radio Polarimetric Observations of the 11 August 1999 Solar Eclipse via the Trieste Solar Radio System.} 463, 595.
    \item \url{https://ssd.jpl.nasa.gov/horizons/}
    \item Leung, C. S., Fok, T. K. T., Hui, K. H. K., Ng, K. W., Lee, C. M., and Chang, S. H. (2022). Solar Eclipse Observations with Small Radio Telescope in Hong Kong in the 21 CM Radio Frequency Band. \textit{Romanian Astronomical Journal}, 32, 35-52.
\end{enumerate}